\part{Laboratory}

# Visualization

## Prerequisites

Before starting to visualize networks, it is necessary to install the package for Social Network Analysis, called `sna`:

```{r message=FALSE, warning=FALSE}
library(sna)
```

## Modifying the layout on KHF network

### Random layout

Let's plot the nodes randomly in the two-dimensional space, with the KHF dataset. 

Notice that in order to build a network, we need an adjacency matrix, that's why the csv is converted into a matrix structure. Then, in order to symmetrize it and make it undirected, it is multiplied for its transpose, to make a self-multiplication, in order to get an undirected network from a directed one (remember that if there's a link going in both sides, we can insert an undirected link between these two vertices).

_For instance, consider the following directed adjacency matrix:_

$$
\left( \begin{array}{ccc}
0 & 1 & 1 \\
1 & 0 & 0 \\
0 & 0 & 1 \end{array} \right)
$$
By computing its transpose and perform the self multiplication we obtain the undirected network (symmetric and with links only whenever the link goes on both sides in the original directed network):

$$
\left( \begin{array}{ccc}
0 & 1 & 1 \\
1 & 0 & 0 \\
0 & 0 & 1 \end{array} \right) \times 
\left( \begin{array}{ccc}
0 & 1 & 0 \\
1 & 0 & 0 \\
1 & 0 & 1 \end{array} \right) = 
\left( \begin{array}{ccc}
0 & 1 & 0 \\
1 & 0 & 0 \\
0 & 0 & 1 \end{array} \right)
$$

In the end it is turned into a network object.

```{r}
# 1. Read in the friendship network for Krackhardt's high-tech managers:
KHF <- as.matrix(read.csv("datasets/Krackhardt_HighTech_Friendship.csv",
                          stringsAsFactors=FALSE, row.names=1))


# 2. Symmetrize the matrix using the minimum approach, so a friendship tie
# is only considered if both agree they are friends:
KHFS <- KHF*t(KHF)

# 3. Turn this into a "network" object:
KHFSn<-as.network(KHFS, directed=F)
```

To save the plot as a tiff file (in the default folder) use the `tiff()` function, which opens an image file,
and finish with `dev.off()`, which closes the image file for changes.

```{r}
# 4. Create and save visualization
# tiff(file="images/Fig_01_KHFS_Random.tiff", 
#      width=7, height=5,
#      units="in", res=900)
par(mar=c(0,0,0,0)) # Margin deletion
gplot(KHFSn,
      gmode="graph",      # undirected network
      mode="random",      # random plotting of nodes
      jitter=F,           # do not allow nodes to be "jittered"
      edge.col="grey70",  # set color of ties
      vertex.col="cornflowerblue",   # set color of nodes
      displaylabels=T,    # indicate that labels should be included
      label.pos=1,        # indicate that labels should be given below points
      label.cex=.7)       # indicate the size of the labels (1 is default)
# dev.off()
```

_`gmode="graph"` is used for **undirected** networks, while `gmode="digraph` is used for **directed** networks. If the input graph is undirected but the selected gmode is for directed networks, then arrows on both sides will be visualized. Also, most of the times the margin deletion is not necessary._

The use of random position may be risky because of links overlapping and too close nodes. 

### Circle Layout

For a circle layout, it is necessary to change `mode` into `"circle"`. 

```{r}
par(mar=c(0,0,0,0))
gplot(KHFSn, 
      gmode="digraph",
      mode="circle",
      jitter=F,
      edge.col="grey70",
      vertex.col="cornflowerblue",
      displaylabels=T,
      label.pos=1,
      label.cex=.7,
      arrowhead.cex = 0.5)
```

### FR Layout


```{r}
par(mar=c(0,0,0,0))
gplot(KHFSn, 
      gmode="graph",
      #layout
      mode="fruchtermanreingold",
      jitter=FALSE,
      #ties
      edge.col="grey80",
      #nodes
      vertex.col="cornflowerblue",
      vertex.cex = 1,
      #labels
      displaylabels=T,
      label.pos=1,
      label.cex=.7)
```

### KHA Network

The following network is denser than the previous, since we multiply the matrix for its transpose, indicating

```{r}
# Read in the advice network for Krackhardt's high-tech managers:
KHA<-as.matrix(read.csv("datasets/Krackhardt_HighTech_Advice.csv",
                        stringsAsFactors=FALSE, row.names=1))

# Symmetrize the matrix using the minimum approach, so an advice tie
# is only considered if both ask each other for advice:
KHAS<-KHA*t(KHA)

# Turn this into a "network" object:
KHASn<-as.network(KHAS, directed=T)

par(mar=c(0,0,0,0))
gplot(KHASn, 
      gmode="graph",
      #layout
      mode="fruchtermanreingold",
      jitter=F,
      #ties
      edge.col="grey70",
      #nodes
      vertex.col="cornflowerblue",
      #labels
      displaylabels=T,
      label.pos=1,
      label.cex=.7)
```
We could also build a function to plot a network: 
```{r}
plot_network = function(network){
    gplot(network, 
      gmode="graph",
      #layout
      mode="fruchtermanreingold",
      jitter=F,
      #ties
      edge.col="grey70",
      #nodes
      vertex.col="cornflowerblue",
      #labels
      displaylabels=T,
      label.pos=1,
      label.cex=.7)
}

# Example of use
plot_network(KHASn)
```

## Layout based on 2 continuous attributes

```{r}
# Read data and convert it into matrix
WPJ <- as.matrix(read.csv("datasets/Wolfe_Primates_JointPresence.csv",
                          stringsAsFactors=FALSE, row.names=1))

# Read attributes
WPAttr <- read.csv("datasets/Wolfe_Primates_Attributes.csv",
                   stringsAsFactors=FALSE, row.names=1)

# Rescale attributes so they range from 0 to 1
WP.AGE <- (WPAttr$AGE-min(WPAttr$AGE))/(max(WPAttr$AGE)-min(WPAttr$AGE))
WP.RANK <- (max(WPAttr$RANK)-WPAttr$RANK)/(max(WPAttr$RANK)-min(WPAttr$RANK))

# Turn the 2 continuous variables into coordinates
WPCOORD <- matrix(c(WP.AGE,WP.RANK),
                  dim(WPJ)[1],2)

# Consider drawing only "relatively strong" ties
WPJ6W <- (WPJ>5)*(WPJ-5) 
# Only consider a tie in tie matrix, but only 
# if major than 5 and then rescale it by removing 5
```

In the next step, we're going to make darker ties for those links where primates interacted more with each other (from grey40 to grey90). 

```{r}
# Create colors (greyscales) for ties
WPJ6W.Color<-WPJ6W
col.grey<-colorRampPalette(c("grey90", "grey40"))
col.greyN<-col.grey(max(WPJ6W)+1)
for (k in (1:max(WPJ6W)))
{
    WPJ6W.Color[WPJ6W==k]<-col.greyN[k+1]
}
```

Now let's start drawing, remembering that:

* coordinates of nodes are given by their rank and their age (attributes): `coord=WPCOORD`;
* the edge color is given by the mapping color based on their number of links: `edge.col=WPJ6W.Color`;
* the color of the vertex indicates the gender of the primate (white for females, black for males): `vertex.col=(WPAttr$GENDER=="male")*9`;
* the added arrows allows us to visualize the cartesian plan. 

```{r}
par(mar=c(0,0,0,0))
gplot(WPJ6W*1.1,
      gmode="digraph", 
      #layout
      coord=WPCOORD, # using the coordinates to place primates 
      jitter=F,
      #ties
      edge.col=WPJ6W.Color,
      edge.lwd=.3,
      #nodes
      vertex.col=(WPAttr$GENDER=="male")*9,
      vertex.cex=0.5, 
      #labels
      displaylabels=T, 
      label.pos=1,
      label.cex=.7,
      arrowhead.cex = 0.4)

# Add arrows
arrows(-.1, -.1, 1.1, -.1, length = 0.1)
arrows(-.1, -.1, -.1, 1.1, length = 0.1)
text(-.1, 1.1, labels="Rank",
     cex=0.8, pos=4)
text(1.1,-.1, labels="Age",
     cex=0.8, pos=3)
```

## Layout where points are grouped based on nominal attribute

First of all, we're going to import the datasets and convert them into networks as usual:
```{r}
# 1. Convert datasets into networks
## Convert the KHA dataset into a network
KHA<-as.matrix(read.csv("datasets/Krackhardt_HighTech_Advice.csv",
                        stringsAsFactors=FALSE, row.names=1))
KHAS<-KHA*t(KHA)
KHASn<-as.network(KHAS, directed=F)

## Convert the KHF dataset into a network
KHF<-as.matrix(read.csv("datasets/Krackhardt_HighTech_Friendship.csv",
                        stringsAsFactors=FALSE, row.names=1))
KHFS<-KHF*t(KHF)
KHFSn<-as.network(KHFS, directed=F)
```

Then, we can create a network with ties within departments to define positions. By importing the KHA dataset and maintaining its attribute, we will maintain the departments and convert them to matrix.  In the end, we maintain only those links where two subjects belong to the same department (`DEPS==t(DEPS)`).

```{r}
# 2. Create a network with ties within department to define positions
KHAttr<-read.csv("datasets/Krackhardt_HighTech_Attributes.csv",
                 stringsAsFactors=FALSE, row.names=1)
DEPS<-matrix(KHAttr$DEPT,nrow(KHA),nrow(KHA))
DEPSIM<-DEPS==t(DEPS)
```

We can get nodes coordinates by plotting them based on their department similarity. Coords may change from an execution to another, but groupings will be the same. In this way, we will place similar nodes next to each other.

```{r}
# 3. Get coordinates
par(mar = c(0,0,0,0))
DEP_COORD<-gplot(DEPSIM, 
                 displaylabels=T)
```

```{r}
# 4. Draw the friendship network using 
#    the coordinates got from nominal friendship
par(mar=c(0,0,0,0))
gplot(KHFSn,
      gmode="graph",
      #layout
      coord=DEP_COORD,
      jitter=F,
      #ties
      edge.col="grey50",
      edge.lwd=.7,
      #nodes
      vertex.col="cornflowerblue",
      #labels
      displaylabels=T, 
      label.pos=1, 
      label.cex=.7)
```


```{r}
par(mar=c(0,0,0,0))
gplot(KHASn,
      gmode="graph",
      #layout
      coord=DEP_COORD,
      jitter=F,
      #ties
      edge.col="grey50",
      edge.lwd=.7,
      #nodes
      vertex.col="cornflowerblue",
      #labels
      displaylabels=T, 
      label.pos=1, 
      label.cex=.7)
```
## Geography - International trade among countries in 1928

In this case, nodes are positioned based on the geographic location of their capitals. Canada and the US have been slightly moved to the West to make the trade between European countries more visible. 

```{r}
# 1. Dataset conversion into network
STE<-as.matrix(read.csv("datasets/Savage_TransactionFlows_ExportsPerc.csv",
                        stringsAsFactors=FALSE, row.names=1))
STAttr<-read.csv("datasets/Savage_TransactionFlows_Attributes.csv",
                 stringsAsFactors=FALSE, row.names=1)

# 2. Consider Latitude and Longitude
LA<-STAttr$Latitude
LO<-STAttr$Longitude

# 3. Move Canada and US to the west
LO[2:3]<-LO[2:3]+40

# 4. Symmetrized using product
STES<-(STE*t(STE))
##  To plot only stronger trades (more than 19 trades)
STESGT20<-round(((STES>19)*(STES-19))^.5)

# 5. Create colors (greyscale) for ties
STESGT20.Color<-STESGT20
col.grey<-colorRampPalette(c("grey80", "grey40"))
col.greyN<-col.grey(max(STESGT20)+1)
for (k in (1:max(STESGT20)))
{
    STESGT20.Color[STESGT20==k]<-col.greyN[k+1]
}
```


```{r}
# 6. Visualizing the map
par(mar=c(0,0,0,0))
gplot(STESGT20, 
      gmode="graph",
      coord=cbind(LO,LA), # Using geographical coordinates to map cities
      jitter=F,
      edge.col=STESGT20.Color,
      edge.lwd=0.4,
      vertex.col="grey90",
      vertex.cex=0.3,
      displaylabels=T, 
      label.cex=.5)
```

## Multidimensional scaling

### MDS on Primates

We can apply the MDS in order to better plot nodes inside the network, by using the default function in R `cmdscale()`.

```{r}
# 1. Rescale values using MDS
WPJS<-log(WPJ+1)
WPJ_CoordMDS<-cmdscale(max(WPJS)*1.001-WPJS, eig=TRUE, k = 2)

# 2. Consider drawing only "relatively strong" ties
WPJ6W<-(WPJ>5)*(WPJ-5)

# 3. Create color for ties
WPJ6W.Color<-WPJ6W
col.grey<-colorRampPalette(c("grey80", "grey30"))
col.greyN<-col.grey(max(WPJ6W)+1)
for (k in (1:max(WPJ6W)))
{
    WPJ6W.Color[WPJ6W==k]<-col.greyN[k+1]
}

# 4. Draw
par(mar=c(0,0,0,0))
gplot(WPJ6W*1.1,
      gmode="graph", 
      #layout
      coord=WPJ_CoordMDS$points,
      jitter=F,
      edge.col=WPJ6W.Color,
      edge.lwd=0.5,
      #nodes
      vertex.col=ifelse(WPAttr$GENDER=="male",4,2),
      vertex.cex=0.8, 
      #labels
      displaylabels=T, 
      label.pos=1,
      label.cex=.7)
```

### MDS on valued trade 
```{r}
STE<-as.matrix(read.csv("datasets/Savage_TransactionFlows_ExportsPerc.csv",
                        stringsAsFactors=FALSE, row.names=1))
# Symmetrized using product
STES<-(STE*t(STE))
# To plot only stronger trade 
STESGT20<-round(((STES>19)*(STES-19))^.5)

# Create colors (greyscale) for ties
STESGT20.Color<-STESGT20
col.grey<-colorRampPalette(c("grey80", "grey40"))
col.greyN<-col.grey(max(STESGT20)+1)
for (k in (1:max(STESGT20)))
{
    STESGT20.Color[STESGT20==k]<-col.greyN[k+1]
}

STESGT20_Coord<-cmdscale((max(STE)*1.002-STE)^2, eig=TRUE, k = 2)
#STESGT20_Coord<-cmdscale(STE-STE, eig=TRUE, k = 2)

par(mar=c(1,1,1,1))
gplot(STESGT20, 
      gmode="graph",
      #layout
      coord=STESGT20_Coord$points,
      jitter=F,
      #ties
      edge.col=STESGT20.Color,
      edge.lwd=0.4,
      #nodes
      vertex.col="grey90",
      vertex.cex=0.8,
      #labels
      displaylabels=T, 
      label.pos=1, 
      label.cex=.7)
```

### MDS on geodesic distances

```{r}
KHA<-as.matrix(read.csv("datasets/Krackhardt_HighTech_Advice.csv",
                        stringsAsFactors=FALSE, row.names=1))
KHAS<-KHA*t(KHA)
KHASn<-as.network(KHAS, directed=F)
GeoD<-geodist(KHASn)
max(GeoD$gdist)
#GeoD$gdist[GeoD$counts==0]<--999
#GeoD$gdist[GeoD$gdist==-999]<-max(GeoD$gdist)
GeoD_Coord<-cmdscale(GeoD$gdist, eig=TRUE, k=2)
GeoD_Coord

par(mar=c(1,1,1,1))
gplot(KHASn,
      gmode="graph",
      #layout
      coord=GeoD_Coord$points,
      jitter=T,
      #ties
      edge.col="grey50",
      edge.lwd=.7,
      #nodes
      vertex.col="cornflowerblue",
      #labels
      displaylabels=T,
      label.cex=.7)
```

## KamadaKawai and FR layout KHFS

### On Simulated data
```{r}
mat8<-matrix(c(0),8,8)
mat8[1,2]<-1
mat8[2,3]<-1
mat8[3,4]<-1
mat8[3,5]<-1
mat8[3,6]<-1
mat8[4,5]<-1
mat8[4,6]<-1
mat8[5,6]<-1
mat8[6,7]<-1
mat8[7,8]<-1
mat8s<-(mat8+t(mat8))>0

gplot(mat8, 
      gmode="graph",
      #layout
      mode="fruchtermanreingold",
      jitter=FALSE,
      #ties
      edge.col="grey70",
      #nodes
      vertex.col="cornflowerblue",
      #labels
      displaylabels=T,
      label.pos=1,
      label.cex=.7)

gplot(mat8, 
      gmode="graph",
      #layout
      mode="kamadakawai",
      jitter=FALSE,
      #ties
      edge.col="grey70",
      #nodes
      vertex.col="cornflowerblue",
      #labels
      displaylabels=T,
      label.pos=1,
      label.cex=.7)
```

### Scientists collaborations

In the next chunk, the aim is to separated into two clusters those scientists that have more than 3 years of experience in their studies from those who do not. As can be seen from the plot, two groups are obtained: one with no edges and the other where every node is connected with the center.

```{r}
BS504Cx<-as.matrix(read.csv("datasets/Borgatti_Scientists504_Attributes.csv",
                            stringsAsFactors=FALSE, row.names=1))
BS504C<-(BS504Cx>3)

par(mar=c(0,0,0,0))
gplot(BS504C, 
      gmode="graph",
      #layout
      mode="kamadakawai",
      jitter=F,
      #ties
      edge.col="grey70", 
      edge.lwd=.1,
      #nodes
      vertex.col="cornflowerblue",
      vertex.cex=.75)
```


### Nodal attributes on KHF

Let's consider scientists' tenure. If we aim to plot the variation in terms of tenure among scientists, size can be a choice:

```{r}
KHF<-as.matrix(read.csv("datasets/Krackhardt_HighTech_Friendship.csv",
                        stringsAsFactors=FALSE, row.names=1))
KHFS<-KHF*t(KHF)
KHAttr<-read.csv("datasets/Krackhardt_HighTech_Attributes.csv",
                 stringsAsFactors=FALSE, row.names=1)

par(mar=c(1,1,1,1))
gplot(KHFS, 
      gmode="graph",
      #layout
      mode="fruchtermanreingold",
      jitter=F,
      #ties
      edge.col="grey30",
      edge.lwd=.4,
      #nodes
      vertex.col="cornflowerblue",
      vertex.cex=KHAttr$TENURE/20+.8,
      #labels
      displaylabels=TRUE,
      label.cex=.7)
```

Now, the same plot is proposed again with:

* level as shape and colour;
* tenure as size.

```{r}
# type sides of nodes
KHF<-as.matrix(read.csv("datasets/Krackhardt_HighTech_Friendship.csv",
                        stringsAsFactors=FALSE, row.names=1))
KHFS<-KHF*t(KHF)
KHAttr<-read.csv("datasets/Krackhardt_HighTech_Attributes.csv",
                 stringsAsFactors=FALSE, row.names=1)

par(mar=c(2,2,2,2))
gplot(KHFS, 
      gmode="graph",
      #layout
      mode="fruchtermanreingold",
      jitter=F,
      #ties
      edge.col="grey30",
      edge.lwd=.4,
      #nodes
      vertex.col=((KHAttr$LEVEL==1)*1+
                    (KHAttr$LEVEL==2)*7+
                    (KHAttr$LEVEL==3)*0),
      # Define symbols
      vertex.sides=((KHAttr$LEVEL==1)*3+
                      (KHAttr$LEVEL==2)*4+
                      (KHAttr$LEVEL==3)*20),
      vertex.cex=.8+KHAttr$TENURE/25,
      #labels
      displaylabels=TRUE,
      label.cex=.7)
```

### Scientists collaboration (more complex)

```{r}
# Gender and tenure with legend
BS504Cx<-as.matrix(read.csv("datasets/Borgatti_Scientists504_Attributes.csv",
                            stringsAsFactors=FALSE, row.names=1))
BS504C<-(BS504Cx>3)

BS504Attr<-read.csv("datasets/Borgatti_Scientists504_Attributes.csv",
                    stringsAsFactors=FALSE, row.names=1)
```


```{r}
# Get the years
Tenure<-(BS504Attr$Years)

# Normalize the tenure by the maximum and consider the integer number of years
TenureA<-(round(10*(Tenure)/max((Tenure))))

# Create a color palette 
colfunc <- colorRampPalette(c("lightpink", "cornflowerblue"))
COLWB<-colfunc(7)

# Assign colors to different tenures
TenureA2<-TenureA
TenureA2[TenureA==0]<-COLWB[1]
TenureA2[TenureA==1]<-COLWB[2]
TenureA2[TenureA==2]<-COLWB[3]
TenureA2[TenureA==3]<-COLWB[4]
TenureA2[TenureA==4]<-COLWB[5]
TenureA2[TenureA %in% c(5,6)]<-COLWB[6]
TenureA2[TenureA %in% c(7,8,9,10)]<-COLWB[7]

# Plot 
par(mar=c(0,0,0,0))
gplot(BS504C, 
      gmode="graph", 
      #layout
      #mode="kamadakawai",
      jitter = F,
      #ties
      edge.col="grey80",
      edge.lwd=.2, 
      #nodes
      vertex.col=TenureA2,
      vertex.cex=1+.7*(2-BS504Attr$Sex), 
      vertex.sides=(BS504Attr$Sex-1)*47+4)

legend("topright",
       legend = c("Colors"," Senior", " Junior", " ","Shapes", " Male (2)", " Female (1)"),
       col = c("white","lightpink","cornflowerblue","white","white","black","black"), 
       bty = "n", pch =c(19,19,19,19,19,19,18),
       pt.cex = c(0,2.1,2.1,0,0,1.7,1.9), 
       cex = 1, 
       text.col = "grey10", 
       horiz = F , 
       inset = c(0.01))
```



### Nodal attributes on PFM

```{r}
PFM<-as.matrix(read.csv("datasets/Padgett_FlorentineFamilies_Marriage.csv",
                        stringsAsFactors=FALSE, row.names=1))

PFMn<-as.network(PFM, directed=F)

# Compute the degree of the network
DPFM<-sna::degree(PFMn)

# Plot the network, where the size relies on the degree of every node
par(mar=c(0,0,0,0))
gplot(PFMn, 
      gmode="graph", 
      #layout
      jitter=F,
      #ties
      edge.col="grey70",
      edge.lwd=.1, 
      #nodes
      vertex.col="cornflowerblue",
      vertex.cex=DPFM/17+.5,
      #labels
      displaylabels=TRUE, 
      label.pos=3, 
      label.cex=DPFM/20+.3, 
      vertex.border="white")
```


## Tie strength on Scientists collaborations

```{r}
BS504C<-as.matrix(read.csv("datasets/Borgatti_Scientists504_Attributes.csv",
                           stringsAsFactors=FALSE, row.names=1))

# Filtering different years of experience
BS504CGT3<-(BS504Cx>3)
BS504CGT5<-(BS504Cx>5)
BS504CGT7<-(BS504Cx>7)
BS504CGT9<-(BS504Cx>9)
```


```{r}
# 3 years of experience
par(mar=c(0,0,0,0))
gplot(BS504CGT3,
      gmode="graph",
      jitter=F,
      #ties
      edge.col="grey70", 
      edge.lwd=.1,
      #nodes
      vertex.col="cornflowerblue",
      vertex.cex=.75)
```


```{r}
# 5 Years of experience
par(mar=c(0,0,0,0))
gplot(BS504CGT5,
      gmode="graph",
      #layout
      jitter=F,
      #ties
      edge.col="grey60", 
      edge.lwd=.1,
      #nodes
      vertex.col="cornflowerblue",
      vertex.cex=.75)
```


```{r}
# 7 Years of experience
par(mar=c(0,0,0,0))
gplot(BS504CGT7,
      gmode="graph",
      jitter=F,
      #ties
      edge.col="grey60", 
      edge.lwd=.1,
      #nodes
      vertex.col="cornflowerblue",
      vertex.cex=.75)
```


```{r}
# 9 years of experience
par(mar=c(0,0,0,0))
gplot(BS504CGT9,
      gmode="graph",
      jitter=F,
      #ties
      edge.col="grey60", 
      edge.lwd=.1,
      #nodes
      vertex.col="cornflowerblue",
      vertex.cex=.75)
```


## Directed networks

```{r}
KHF<-as.matrix(read.csv("datasets/Krackhardt_HighTech_Friendship.csv",
                        stringsAsFactors=FALSE, row.names=1))
KHFn<-as.network(KHF, directed=T)
```


```{r message=FALSE, warning=FALSE, include=FALSE}
# Saving coordinates
COOKHF<-gplot(KHFn,
              gmode="digraph",    
              #layout
              jitter=F,           # do not allow nodes to be "jittered"
              #ties
              edge.col="grey40",
              arrowhead.cex=.7,
              # set color of ties
              #nodes
              vertex.col="grey90",   # set color of nodes
              vertex.cex=1.4,
              #labels
              displaylabels=T,    # indicate that labels should be included
              label.pos=5,        # indicate that labels should be given below points
              label.cex=.5)       # indicate the size of the labels (1 is default)
```


```{r}
# Plotting points based on their coordinates
par(mar=c(0,0,0,0))
gplot(KHFn,
      gmode="digraph",  
      coord=COOKHF,
      #layout
      jitter=F,           # do not allow nodes to be "jittered"
      #ties
      edge.col="grey30",
      edge.lwd=0.2,
      usecurve=T,
      edge.curve=.04, 
      arrowhead.cex=.4,
      
      #nodes
      vertex.col="lightpink",   # set color of nodes
      vertex.cex=1.4,
      #labels
      displaylabels=T,    # indicate that labels should be included
      label.pos=5,        # indicate that labels should be given below points
      label.cex=.5)       # indicate the size of the labels (1 is default)
```