# Centrality Measures


```{r, fig.align="center"}
library(sna)
# FLORENTINE FAMILIES
PFM<-as.matrix(read.csv("datasets/Padgett_FlorentineFamilies_Marriage.csv",
                        stringsAsFactors=FALSE, row.names=1))
PFMn<-as.network(PFM, directed=F)
par(mar=c(0,0,0,0))
gplot(PFMn, 
      gmode="graph",
      jitter=F,
      edge.col="grey80",
      vertex.cex = 1,
      vertex.col="cornflowerblue",
      displaylabels=T,
      label.pos=1,
      label.cex=.7)
```

The following plot considers the family's wealth, represented both by size and colour variation.

```{r, fig.align="center"}
# Add attributes file and use wealth to change size of nodes (vertex.cex)
PFA<-read.csv("datasets/Padgett_FlorentineFamilies_Attributes.csv",
               stringsAsFactors=FALSE, row.names=1)

# Color palette
n_colors<-max(PFA$Priors)-min(PFA$Priors)+1
colfunc <- colorRampPalette(c("#FFD670", "#70D6FF"))
colors<-colfunc(n_colors)

par(mar=c(0,0,0,0))
gplot(PFMn, 
      gmode="graph",
      jitter=F,
      edge.col="grey70",
      vertex.col=colors[PFA$Priors+1],
      vertex.cex=PFA$Wealth/80+1,
      displaylabels=T,
      mar = c(0,0,0,0),
      label.pos=1,
      label.cex=.6)
```

First, we will compute some centrality measures, such as degree, betweenness, Bonacich beta centrality and the constraint index. 
```{r}
# Calculate centrality measures
## Degree
sna::degree(PFMn, gmode="graph")

## Betweenness centrality
sna::betweenness(PFMn, gmode="graph", cmode="undirected")

## Bonacich Power Centrality
sna::bonpow(PFMn, gmode="graph", exponent=0)

## Constraint index
library(igraph)
PFM_i<-graph_from_adjacency_matrix(as.matrix(PFM),mode="undirected", diag=F)
constraint(PFM_i)
```
Then, some statistical tests are applied to evaluate the correlation between degree, wealth and the number of priors for each family. 

```{r}
# Statistical tests for significance
PFMn.Deg<-sna::degree(PFMn, gmode="graph")

cor.test(PFMn.Deg,PFA$Priors) # Number of families vs Priors
cor.test(PFMn.Deg,PFA$Wealth) # Number or families vs Wealth
cor.test(PFA$Priors,PFA$Wealth) # Priors vs Wealth
```

Also, linear models can be used, paying attention to the fact that we detain a few data and the model may not be accurated and general. 

```{r}
# Linear Models
## One of them
M1<-lm(PFMn.Deg~PFA$Priors)
summary(M1)
## Both of them
M2<-lm(PFMn.Deg~PFA$Priors+PFA$Wealth)
summary(M2)
```

Since there's no right parameter to set as exponent, we can iterate over some possible values and choose the one that gives the wanted results: if negative, we repulse other people; if positive, we aim to attract people and see if our connections propagate over the network. If close to 0, we just consider direct links. 

```{r}
# Bonacich Centrality
exponents = c(seq(-0.5,0.5,0.1))
exp = c()
bonpow_results = c()
for(e in exponents){
   exp = append(exp, rep(e,16))
   bonpow_results = append(bonpow_results,
                           sna::bonpow(PFA, gmode="graph", exponent=e))
}
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(kableExtra)
kbl(data.frame(cbind(Exponent = exp,
                 Bonpow = round(bonpow_results[1:11*16], 3),
                 Family = rep(rownames(PFA),11))) %>%
   filter(Family %in% c("MEDICI","PUCCI","GUADAGNI"),
          Exponent %in% c(-0.5,0,0.5))%>%
   arrange(Family), 
   booktabs = T, 
   caption = "Three families Bonacich Beta centrality varying exponent")
```

