# Subgroups and equivalence

Suppose we focus on the following network:

```{r echo=FALSE}
library(sna)

network<-matrix(c(
  0,1,1,0,0,1,1,0,0,0,0,0,0,0,0,0,0,0,0,
  1,0,1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,
  1,1,0,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,
  0,0,1,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,
  0,0,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,
  1,1,1,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,
  1,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,
  0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,
  0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,
  0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,
  0,0,0,0,0,0,0,0,1,1,0,1,0,0,0,0,0,0,0,
  0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,
  0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,
  0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,1,1,
  0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,1,0,0,0,
  0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,1,0,0,
  0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,1,0,
  0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,1,0,1,
  0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,1,0),19,19)

par(mar=c(0,0,0,0))
gplot(network,
      displaylabels=TRUE,
      edge.lwd=0.5,
      vertex.lty = 0.5,
      edge.col = "grey60",
      vertex.col = "cornflowerblue",
      vertex.cex = 1,
      label.cex = 0.7,
      usearrows=FALSE, 
      gmode="graph"
)
```

We can compute the census of the cliques inside this network. In particular, we can count per each node and per each $k$-clique how many cliques it belongs to.

```{r}
clique.census(network, mode = "graph")$clique.count
```

Consider on the other side this network:

```{r echo=FALSE, out.width="80%"}
# Equivalence
network_2<-matrix(c(
  0,0,0,0,0,0,0,0,
  0,0,0,0,0,0,0,0,
  1,0,0,0,1,1,0,0,
  0,1,0,0,1,1,0,0,
  0,1,0,0,0,1,0,0,
  0,1,0,0,1,0,0,0,
  0,0,0,0,0,0,0,0,
  0,0,0,0,0,0,0,0),8,8,byrow=T)

par(mar=c(0,0,0,0))
gplot(network_2,
      displaylabels=TRUE,
      edge.lwd=0.5,
      vertex.lty = 0.5,
      edge.col = "grey60",
      vertex.col = "cornflowerblue",
      vertex.cex = 1,
      label.cex = 0.7, 
      gmode="digraph")
```

Then the Hamming distance can be computed. Look at $7$ and $8$: they are both isolated and their Hamming distance amounts to 0. It basically represents how many edges nodes do not share with the other node. For instance, $3$ has 3 links, while $5$ has $5$ links. They share a common link to $8$ and they are linked, therefore their distance is $1+3 = 4$.

```{r}
# Hamming Structural Equivalence
network_2_SEH<-sedist(network_2, method="hamming")
network_2_SEH
```


```{r}
## Clustering on hamming distance
network_2_SEHD<-as.dist(network_2_SEH)
network_2_SEHD_HC<-hclust(network_2_SEHD,method="complete")
plot(network_2_SEHD_HC)
```

Same happens with the euclidean distance, which instead of absolute values considers the squared ones. 
```{r}
# Euclidean Structural Equivalence
network_2_SEE<-sedist(network_2, method="euclidean")
network_2_SEE
```

```{r}
## Clustering on euclidean distance
network_2_SEED<-as.dist(network_2_SEE)
network_2_SEED_HC<-hclust(network_2_SEED,method="complete")
plot(network_2_SEED_HC)
```
