# Dyads and triads

## Dyads

```{r echo=FALSE, out.width="80%", fig.cap = "Example of a directed network"}
mat6<-matrix(c(0,0,0,1,0,0,
               0,0,1,0,0,0,
               0,1,0,0,0,0,
               1,1,1,0,1,1,
               0,0,1,1,0,1,
               0,0,0,0,1,0),6,6, byrow=T)
par(mar=c(0,0,0,0))
gplot(mat6, 
      displaylabels = T,
      label.pos = 3,
      edge.col= "grey60",
      vertex.col = "cornflowerblue",
      label.cex = 1,
      vertex.cex = 1.5)
```

The `dyad.census()` function returns the number of mutual, asymmetric and null edges.

```{r}
# Dyad Census
sna::dyad.census(mat6, g=NULL)
```
In order to compute the reciprocity, there are two variants:

- the first one is the ratio of mutuals $M$ and null edges $N$ over the total amount of edges possible ($M+A+N$):

```{r}
sna::grecip(mat6,measure="dyadic")
```

- the second version just considers mutuals and asymmetric (i.e. $2M/(2M+A)$):

```{r}
sna::grecip(mat6,measure="edgewise")
```

Also, igraph allows to compute the reciprocity but only with the second modality ($2M/(2M+A)$):

```{r message=FALSE, warning=FALSE}
# With igraph
library(igraph)
mat6i<-graph_from_adjacency_matrix(mat6,mode=c("directed"),diag=F)
igraph::reciprocity(mat6i)
```

## Triads

```{r echo=FALSE, out.width="80%"}
mat6<-matrix(c(0,0,0,1,0,0,
               0,0,1,0,0,0,
               0,1,0,0,0,0,
               1,1,1,0,1,1,
               0,0,1,1,0,1,
               0,0,0,0,1,0),6,6, byrow=T)

par(mar=c(0,0,0,0))
gplot(mat6, 
      displaylabels = T,
      label.pos = 3,
      edge.col= "grey60",
      vertex.col = "cornflowerblue",
      label.cex = 1,
      vertex.cex = 1.5)
```

Let's change network and compute the triad census. The function `triad.census()` will return the number of triads per type according to the MAN nomenclature. 
```{r}
# Triad census
sna::triad.census(mat6)
```

For instance, there are 3 null edges ($(6,1), (1,2), (2,6)$) and 1 210 ($4,5,6$). The transitivity amounts to `r sna::gtrans(mat6)`, which is highly significant. We can test it creating $1,000$ permutations of the graph and computing the transitivity of each of them. The probability of forming an edge equals the density of the original matrix. 

```{r}
sna::gtrans(mat6)
```
```{r}
RG100<-sna::rgraph(20,1000,tprob=sna::gden(mat6))
hist(sna::gtrans(RG100), breaks = 20, col="lightpink",
     main = "Random graphs transitivity")
abline(v = sna::gtrans(mat6), col = "red", lty = 2, lwd = 2)
```